Learning a functional distance between organizations with unsupervised embeddings of scientific mobility

### 2020-07-15 paper/current/main.tex
edit till right before conclution

%
% Figure - SemAxis results
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_fig.pdf}
	\caption{
		\textbf{Embedding captures latent geography and prestige hierarchy.}
		\textbf{a.} Illustrates SemAxis projection along two axes,California and Massachusetts and for the top five-to geographically-matched bottom five universities ranked by the 2018 Times Higher Education ranking of U.S. Universities.
		Points correspond to organizations, and a sample of states are highlighted.
		Full organization names listed in Table~\ref{table:supp:orglabels}.
		\textbf{b.} Comparison between the ranking of organizations by their rank in the Times ranking and the SemAxis rank derived from the similarity to the \textit{Elite} end of the axis prestige axis \textit{a}.
		White points are those top and bottom five universities used to define the poles of the axis.
	  	Even when considering only a total of ten organization vectors, the estimate of the Spearman's rank correlation between the SemAxis and Times ranking is 0.73 (n = 145), and increases if controlling for the number of top-and-bottom ranked universities (Fig.~\ref{fig:supp:semaxis_compare}).
	}
	\label{fig:semaxis}
\end{figure}

>>>>

%
% Figure - SemAxis results
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_fig.pdf}
	\caption{
		\textbf{Embedding captures latent geography and prestige hierarchy.}
		\textbf{a.} Illustration of SemAxis projection along two axes;  \textit{latent geographical axis}, from California to Massachusetts (left to right) and \textit{prestige axis}, from the top five to geographically-matched bottom five universities ranked by the 2018 Times Higher Education ranking of U.S. Universities (top to bottom).
		Points correspond to organizations, and a sample of states are highlighted.
		Full organization names listed in Table~\ref{table:supp:orglabels}.
		\textbf{b.} Comparison between the ranking of organizations by their rank in the Times ranking and the SemAxis rank derived from the similarity to the \textit{Elite} end of the axis prestige axis \textit{a}.
		White points are those top and bottom five universities used to define the poles of the axis.
	  	Even when considering only a total of ten organization vectors, the estimate of the Spearman's rank correlation between the SemAxis and Times ranking is 0.73 (n = 145), and it increases if we include more top-and-bottom ranked universities (Fig.~\ref{fig:supp:semaxis_compare}).
	}
	\label{fig:semaxis}
\end{figure}
